### 2016-12-23 local-capability-machine.tex
added local requirement to points to definition
added lemma about stack capability in value relation, a bit more of f3 proof

            Let $W' \futurestr W$ be given and show
            \[
              \npair{(\start_\malloc,\addrend_\malloc,\start_\malloc+\olf)} \in \entryCond{}(\glob)(W')
            \]
            to this end let $W'' \futurestr W'$ and $n' < n$ be given and show
            \[
              \npair[n']{\updatePcPerm{c_\adv}} \in \stder(W'')
            \]
            This follows from the FTLR if we can show
            \[
              \npair[n']{\start_\malloc,\addrend_\malloc} \in \readCond{}(\glob)(W'')
            \]
            $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv}$ governs the adversary, so the result follows from Lemma~\ref{lem:nwlp-subset-pwl}.
          \item $\npair[n'-1]{c_\malloc} \in \stdvr(W)$\\
            Follows from the malloc specification.
            \lau{I don't think this is actually the case at the moment. I guess we either need to show this based on the specification or just require it.}
        \end{enumproof}
    \end{enumproof}
  \item Hyp-Callee\\
    Assume
    \begin{itemize}
    \item $\ms_\stk |_{\start_stk+1,\addrend_\stk} = \ms_{\mathit{act}} \uplus \ms_{\mathit{unused}}$
    \item $W' = \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}'}$ unused}$
    \item $\forall a \in \dom(\ms_{\var{unused}}') \ldotp \ms''(a) = 0$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_, r \mapsto \reg(r)]$ 
    \item $(n,c_{\mathit{ret}}) \in \stdvr(W')$
    \end{itemize}
    where $\ms_{\mathit{act}}$ is the on stack activation code for this $\mathtt{scall}$.
  \item Hyp-Cont\\
    % TODO
\end{enumproof}

@@

\begin{definition}
  We say that $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  iff
  \begin{itemize}
  \item $\reg(r_\stk) =((\rwlx,\_),b_\stk,e_\stk,a_\stk)$
  \item $\dom(\ms_{\mathit{unused}}) = [a_\stk+1,\cdots,e_\stk]$
  \item $\dom(\ms_\stk) = [b_\stk,\cdots,a_\stk]$
  \item $b_\stk - 1\leq a_\stk$
  \end{itemize}
\end{definition}

@@

\begin{lemma}[Anti-reduction for $\observations$]
\label{lem:anti-red-obs}
  \begin{align*}
    & \forall n,i,\reg, \reg', \ms, \ms', \ms_r, W \ldotp\\
    & \quad (\forall \ms_f \ldotp (\reg,\ms \uplus \ms_r \uplus \ms_f) \step[i] (\reg',\ms' \uplus \ms_r \uplus \ms_f)) \land \npair[n-i]{(\reg',\ms')} \in \observations(W) \\
    & \qquad \Rightarrow \npair{(\reg,\ms \uplus \ms_r)} \in \observations(W)
  \end{align*}

>>>>

            Let $W' \futurestr W$ be given and show
            \[
              \npair{(\start_\malloc,\addrend_\malloc,\start_\malloc+\olf)} \in \entryCond{}(\glob)(W')
            \]
            to this end let $W'' \futurestr W'$ and $n' < n$ be given and show
            \[
              \npair[n']{\updatePcPerm{c_\adv}} \in \stder(W'')
            \]
            This follows from the FTLR if we can show
            \[
              \npair[n']{\start_\malloc,\addrend_\malloc} \in \readCond{}(\glob)(W'')
            \]
            $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv}$ governs the adversary, so the result follows from Lemma~\ref{lem:nwlp-subset-pwl}.
          \item $\npair[n'-1]{c_\malloc} \in \stdvr(W)$\\
            Follows from the malloc specification.
            \lau{I don't think this is actually the case at the moment. I guess we either need to show this based on the specification or just require it.}
        \end{enumproof}
    \end{enumproof}
  \item Hyp-Callee\\
    Assume
    \begin{itemize}
    \item $\dom(\ms_\stk |_{\start_stk+1,\addrend_\stk}) = \dom(\ms_{\mathit{act}} \uplus \ms_{\mathit{unused}})$
    \item $W' = \revokeTemp{W}[\iota^{\sta}(\temp,[\start_\stk \mapsto 1]\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$
    \item $\memSat[n-i-1]{\ms''}{W'}$
    \item $\reg'' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}'}$ unused}$
    \item $\forall a \in \dom(\ms_{\var{unused}}') \ldotp \ms''(a) = 0$
    \item $\reg''= \reg_0[\pcreg\mapsto\updatePcPerm{\reg'(r)},r_0 \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_, r \mapsto \reg'(r)]$ 
    \item $\npair[n-i-1]{c_{\mathit{ret}}} \in \stdvr(W')$
    \end{itemize}
    for some $\ms_{\mathit{act}}$, $\ms_{\mathit{unused}}$, $\ms'$, $\reg''$, $c_{\mathit{ret}}$.

    Using the FTLR, we get $\npair[n-i-1]{\updatePcPerm{c_\adv}} \in \stder(W')$, from
    \begin{enumproof}
      \item $\memSat[n-i-1]{\ms''}{W'}$ : By the above assumptions
      \item $\npair[n-i-1]{\reg''} \in \stdvr(W')$:\\
        show
        \begin{enumproof}
          \item $\npair[n-i-1]{c_{\mathit{ret}}} \in \stdvr(W')$ : by above assumptions.
          \item $\npair[n-i-1]{reg''(r_\stk)} \in \stdvr(W')$ : by Lemma~\ref{lem:stack-cap-vr}.
          \item $\npair[n-i-1]{c_\adv} \in \stdvr(W')$ : follows from \ref{eq:f3:adv-in-stder}.
          \item The remaining registers we need to consider contain 0 and are thus trivial to show.
        \end{enumproof}
    \end{enumproof}
    we get
    \[
      \npair[n-i-1]{(\ms'',\reg'')} \in \observations(W')
    \]
  \item Hyp-Cont\\
    % TODO
\end{enumproof}

@@

\begin{definition}
  We say that $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  iff
  \begin{itemize}
  \item $\reg(r_\stk) =((\rwlx,\local),b_\stk,e_\stk,a_\stk)$
  \item $\dom(\ms_{\mathit{unused}}) = [a_\stk+1,\cdots,e_\stk]$
  \item $\dom(\ms_\stk) = [b_\stk,\cdots,a_\stk]$
  \item $b_\stk - 1\leq a_\stk$
  \end{itemize}
\end{definition}

@@

\begin{lemma}[Anti-reduction for $\observations$]
\label{lem:anti-red-obs}
  \begin{align*}
    & \forall n,i,\reg, \reg', \ms, \ms', \ms_r, W \ldotp\\
    & \quad (\forall \ms_f \ldotp (\reg,\ms \uplus \ms_r \uplus \ms_f) \step[i] (\reg',\ms' \uplus \ms_r \uplus \ms_f)) \land \npair[n-i]{(\reg',\ms')} \in \observations(W) \\
    & \qquad \Rightarrow \npair{(\reg,\ms \uplus \ms_r)} \in \observations(W)
  \end{align*}
\end{lemma}

\begin{lemma}[Stack capability in value relation]
  \label{lem:stack-cap-vr}
  \begin{align*}
    & \pointstostack{\reg}{\ms'}{\ms} \land \\
    & (\exists r \ldotp W(r) = \iota^\pwl (\dom(\ms))) \\
    & \quad \Rightarrow \reg(r_\stk) \in \stdvr(W)
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stack-cap-vr}]
  Say 
\[
  \reg(r_\stk) = c_\stk = ((\rwlx,\local),\start,\addrend,\_)
\]
  Show
  \begin{enumproof}
    \item $\npair{(\start,\addrend)} \in \readCond{}(\local)(W)$ : \label{pf:stack-cap-read}\\
      Amounts to
      \[
        \iota^\pwl (\dom(\ms)) \nsubsim \iota^\pwl_{\start,\addrend}
      \]
      which is true as they are even equal.
    \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\local)(W)$ : \label{pf:stack-cap-write}\\
      Amounts to
      \[
        \iota^\pwl (\dom(\ms)) \nsupsim \iota^\pwl_{\start,\addrend}
      \]
      which is true as they are even equal.
    \item $\npair{(\rwlx,\start,\addrend)} \in \execCond{}(\local)(W)$ : \label{pf:stack-cap-exec}\\
      Let $n' < n$, $W' \futurewk W$, and $a\in \dom(\start,\addrend)$ be given and show
      \[
        \npair[n']{((\rwlx,\local),\start,\addrend,a)} \in \stder(W')
      \]
      to this end use the FTLR. To do so, we need to show
      \begin{itemize}
        \item $\npair[n']{(\start,\addrend)} \in \readCond{}(\local)(W')$
        \item $\npair[n']{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\local)(W')$
      \end{itemize}
      As we are considering a public future world, some region still contains $\iota^\pwl (\dom(\ms))$, so it is the same argument as \ref{pf:stack-cap-read} and \ref{pf:stack-cap-write}, respectively.
    \item $\npair{(\rwx,\start,\addrend)} \in \execCond{}(\local)(W)$ : \\
      Same argument as \ref{pf:stack-cap-exec}, but also use \ref{lem:nwl-subset-pwl}.
    \item $\npair{(\exec,\start,\addrend)} \in \execCond{}(\local)(W)$
      Same argument as \ref{pf:stack-cap-exec}.
  \end{enumproof}
\end{proof}
